The Accuracy of KNN, decision tree, random forest, SVM, neural network, naive Bayes classifier and PLA for early Prediction of Diabetes

### 2023-04-02 hw1/paper/main.tex
update KNN-ANNOY

\section*{abstract}
  This work compares the accuracy of some classifiers for early the prediction of diabetes. More specifically, 
  the research compares the accuracy of k-nearest neighbors (KNN) algorithm, decision tree, random forest, 
  support vector machine (SVM), neural network, naive Bayes classifier, and perceptron learning algorithm (PLA) on the prediction of diabetes, which 
  the dataset is collected with eight features, times of pregnancy, concentration of glucose in blood, blood 
  pressure, skin thickness,  concentration of insulin in blood, body mass index (BMI), the value of diabetes 
  pedigree function and age.

@@

\section{KNN}
  The rough process of KNN is described as follow: suppose that there is a dataset which contain $N$ data point, denoted as 
  $(X_i,Y_i)$ where $X_i$ is the features of the i-th individuals data and $Y_i$ is the class label of it. Now 
  a data with unknown class label is given, denoted $(X, Y)$. By a preset distance function $d(P, Q)$, ordering the dataset 
  as $(X_{(1)}, Y_{(1)}), (X_{(2)}, Y_{(2)}), \cdots, (X_{(N)}, Y_{(N)})$ where $d(X_{(1)}, X)\leq d(X_{(2)}, X)\leq\cdots\leq d(X_{(N)}, X)$. 
  Pick the $k$-first class labels to determine the unknow class label, $Y$.

>>>>

\section*{Abstract}
  This work compares the accuracy of some classifiers for early the prediction of diabetes. More specifically, 
  the research compares the accuracy of k-nearest neighbors (KNN) algorithm, decision tree, random forest, 
  support vector machine (SVM), neural network, naive Bayes classifier, and perceptron learning algorithm (PLA) on the prediction of diabetes, which 
  the dataset is collected with eight features, times of pregnancy, concentration of glucose in blood, blood 
  pressure, skin thickness,  concentration of insulin in blood, body mass index (BMI), the value of diabetes 
  pedigree function and age.

@@

\section{KNN}
  \rm{The} rough process of KNN algorithm is described as follow: suppose that there is a dataset which contain $N$ data point, denoted as 
  $(X_i,Y_i)$ where $X_i$ is the features of the i-th individuals data and $Y_i$ is the class label of it. Now 
  a data with unknown class label is given, denoted $(X, Y)$. By a preset distance function $d(P, Q)$, ordering the dataset 
  as $(X_{(1)}, Y_{(1)}), (X_{(2)}, Y_{(2)}), \cdots, (X_{(N)}, Y_{(N)})$ where $d(X_{(1)}, X)\leq d(X_{(2)}, X)\leq\cdots\leq d(X_{(N)}, X)$. 
  Pick the $k$-first class labels to determine the unknow class label, $Y$.

  The algorithm to find $k$ nearest neighbors is the soul of KNN algorithm. The naive way to do that is brute force. By calculating every 
  distance between the dataset and the undetermined data, the desired class can be easily obtained. The time complexity of brute force is $O(n)$. 
  Another way to find $k$ nearest neighbors is approximate nearest neighbors oh yeah (ANNOY). This approximate algorithm is used at Spotify 
  for music recommendations. The process of ANNOY is described follow: In every iteration, two points are randomly chosen, denoted $\vec x_1,\vec x_2$, 
  and the hyperplane in the middle, whose equation is $\vec n^T\vec x=(\vec x_1-\vec x_2)^T\vec x=(\vec x_1-\vec x_2)^T(\vec x_1+\vec x_2)/2=b$ 
  separates all the points in dataset into two kind, "below" ($\vec n^T\vec x<b$) or "above" ($\vec n^T\vec x>b$). Also, in every iteration, a 
  binary tree structure is constructed whose left child contains all the points "below" the hyperplane and right child contains all the points "above". 
  The end condition is when a side of hyperplane contains points no more than $M$, which is a preset parameter. 
  When query a $k$ nearest neighbors of a point, recursively determine if the point "below" or "above" the hyperplane until reaching the leaf node. 
  The time complexity of construction is $O(n)$, and the time complexity of query is $O(\log n)$.
  But since the region searched may have less $k$ points, the search path shall cover both nodes if the point is too close to the hyperplane. This 
  techniques though may increase the search time, still, it can greatly increase the accuracy of searching.
